Model LF

### 2022-12-16 paper version 2.Rmd
Commit

```{r}
plot(((max_dp_01 - max_dp_bs1) / max_dp_bs1), col= "black", xlab= "Year", ylab= "% Change in maximum level of income insurance", main= "Maximum level of incom insurance");
grid()
```

plot(((dp_person_01 - dp_person_bs1) / dp_person_bs1)*100, col= "black", xlab= "Year", main= "Income insurance", ylab= "% Change in avg income insurance");
grid()

plot(((komp_r_01 - komp_r_bs1) / komp_r_bs1)*100, col= "black", xlab= "Year", main= "Compensation rate", ylab= "% Change in compensation rate");
grid()
```

plot(((yk_ds_01 - yk_ds_bs1) / yk_ds_bs1)*100, col= "black", xlab= "Year", main="GDP", ylab= "% Change in gdp");
grid()

plot(((emp_01 - emp_bs1) / emp_bs1)*100, col= "black", xlab= "Year", main= "Employment", ylab= "% Change in employment");
grid()
```

Effect on employment:

```{r}
plot((unemp_01-unemp_bs1)*1000, col= "red")
```

```{r}
plot((nl_g_01-nl_g_bs1), col= "red")
```

@@

>>>>

@@

## Plot

```{r}
plot(((yk_ds_01 - yk_ds_bs1) / yk_ds_bs1)*100, col= "blue", xlab= "Year", ylab= "% Change in GDP", main= "GDP", ylim= c(-0.13, 0.06));
lines(((yk_ds_02 - yk_ds_bs2) / yk_ds_bs2)*100, col= "green");
lines(((yk_ds_03 - yk_ds_bs3) / yk_ds_bs3)*100, col= "red");
legend("top", legend=c("All channels","Except LF Channel", "Except LF and Wage channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green","red"));
grid()
```

```{r}
plot(((nl_g_01 - nl_g_bs1)), col= "blue", xlab= "Year", ylab= "Change in Government net lending", main= "Change in Government net-lending", ylim= c(-500, 2500));
lines(((nl_g_02 - nl_g_bs2)), col= "green");
lines(((nl_g_03 - nl_g_bs3)), col= "red");
legend("left", legend=c("All channels","Except LF Channel", "Except LF and Wage channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","green","red"));
grid()
```

```{r}
plot(((unemp_01 - unemp_bs1)*1000), col= "blue", xlab= "Year", ylab= "Change in unemployment (people)", main= "Sensitivity of Unemployment", ylim= c(-300,3000));
lines(((unemp_02 - unemp_bs2)*1000), col= "green");
lines(((unemp_03 - unemp_bs3)*1000 ), col= "red");
legend("left", legend=c("All channels","Except LF Channel", "Except LF and Wage channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue", "red", "green"));
grid()
```
